Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-28 Manuscript/manuscript.Rmd
changed methods/results headers to sentence case

# METHODS

@@

## GENOMIC ANNOTATION DATA

@@

## Machine learning FRAMEWORK FOR TAD BOUNDARY PREDICTION

@@

### DATA RE-SAMPLING

@@

### FINAL MODEL ASSESSMENT AND PERFORMANCE

@@

### FEATURE REDUCTION

@@

## USING OPTIMALLY BUILT RANDOM FOREST CLASSIFIERS FOR MORE PRECISE TAD BOUNDARY PREDICTION

@@

# RESULTS

## A RESOLUTION-SPECIFIC APPROACH FOR PREDICTING TAD BOUNDARIES

@@

## THREE TYPES OF PREDICTORS DEFINE THE ASSOCIATIONS BETWEEN TAD BOUNDARY REGIONS AND GENOMIC ANNOTATIONS

@@

## TAD VS. NON-TAD BOUNDARY CLASS IMBALANCE IS SEVERE IRRESPECTIVELY OF Hi-C DATA RESOLUTION

@@

## ENSEMBLE FRAMEWORK FOR TAD BOUNDARY PREDICTION

@@

## SMOTE RESAMPLING, DISTANCE-BASED ASSOCIATIONS OF TAD BOUNDARIES AND GENOMIC ANNOTATIONS, AND 10KB RESOLUTION OF HI-C DATA PROVIDED OPTIMAL MODEL PERFORMANCE

@@

## TRANSCRIPTION FACTOR BINDING SITES OUTPERFORM OTHER ANNOTATION-SPECIFIC MODELS

@@

## PREDICTIVE IMPORTANCES CONFIRMED BIOLOGICAL FUNCTIONALITY OF CTCF, RAD21, SMC3, and ZNF143 AT TAD BOUNDARIES

@@

## PREDICTIVE MODELING DEFINES PRECISE AND BIOLOGICALLY RELEVANT LOCATION OF TAD BOUNDARIES

>>>>

# Methods

@@

## Genomic annotation data

@@

## Machine learning framework for TAD boundary prediction

@@

### Data re-sampling

@@

### Final model assessment and performance

@@

### Feature reduction

@@

## Using optimally built random forest classifiers for more precise TAD boundary prediction

@@

# Results

## A resolution-specific approach for predicting TAD boundaries

@@

## Three types of predictors define the associations between TAD boundary regions and genomic annotations

@@

## TAD vs. non-TAD boundary class imbalance is severe irrespectively of Hi-C data resolution

@@

## Ensemble framework for TAD boundary prediction

@@

## SMOTE re-sampling, distance-based associations of TAD boundaries and genomic annotations, and 10 kb resolutions of Hi-C data provided optimal model performance

@@

## Transcription factor binding sites outperform other annotation-specific models

@@

## Predictive importances confirmed biological functionality of CTCF, RAD21, SMC3, and ZNF143 at TAD boundaries

@@

## Predictive modeling defines precise and biologically relevant location of TAD boundaries
